New catch functions from CATCH.nc file

### 2023-05-17 NewCatchWorkflow.Rmd
update with all 3 models matching

Only NOBA first, this one sacc30 with climate, different from sacc38 in mskeyrun without

```{r}

@@

## CC

@@

source(atlmod)

@@

  catchtons <- load_nc_catchtons(dir = dir,
                                 file_nc = nc_catch,
                                 file_fish = file_fish,
                                 bps = bps,
                                 fgs = fgs,
                                 select_groups = select_groups,
                                 select_variable = "Catch",
                                 check_acronyms = TRUE,
                                 bboxes = boxes)
  #if(verbose) message("Catch tons read in.")

@@

aggcatchtons <- catchtons %>%
  dplyr::select(-agecl) %>%
  dplyr::group_by(species, fleet, time) %>%
  dplyr::summarise(totcatch = sum(atoutput)) %>%
  dplyr::mutate(year = ceiling(time/stepperyr))

@@

txtCatchtons <- atlantisom::load_catch(d.name, catch.file, fgs) %>%
  dplyr::filter(species %in% select_groups) %>%
  dplyr::mutate(year = time/365) %>%
  dplyr::left_join(dplyr::select(fgs, Code, Name), by = c("species" = "Name"))

comparetons <- txtCatchtons %>%
  dplyr::left_join(yearcatchtons, by = c("Code" = "species", "year" = "year")) %>%
  ggplot2::ggplot() +
  geom_line(aes(year, atoutput)) +
  geom_point(aes(year, yeartot), color = "blue", alpha = 0.2) +
  facet_wrap(~species, scales="free_y")

# looks like a match!               
comparetons
```

>>>>

For all plots, the total catch derived from CATCH.txt is considered correct, and is represented by the black line. The total catch summed across polygon, subannual timestep and fleet is in blue.

Only NOBA first, this one is model sacc30 with climate, different from sacc38 in `mskeyrun` without climate:

```{r, message=FALSE, warning=FALSE}

@@

@@

comparecatch <- function(atlmod, select_groups, stepperyr) {
  source(atlmod, local = TRUE)

@@

  catchtons <- load_nc_catchtons(
    dir = dir,
    file_nc = nc_catch,
    file_fish = file_fish,
    bps = bps,
    fgs = fgs,
    select_groups = select_groups,
    select_variable = "Catch",
    check_acronyms = TRUE,
    bboxes = boxes
  )
  #if(verbose) message("Catch tons read in.")

@@

  aggcatchtons <- catchtons %>%
    dplyr::select(-agecl) %>%
    dplyr::group_by(species, fleet, time) %>%
    dplyr::summarise(totcatch = sum(atoutput)) %>%
    dplyr::mutate(year = ceiling(time / stepperyr))

@@

  txtCatchtons <- atlantisom::load_catch(d.name, catch.file, fgs) %>%
    dplyr::filter(species %in% select_groups) %>%
    dplyr::mutate(year = time / 365) %>%
    dplyr::left_join(dplyr::select(fgs, Code, Name), by = c("species" = "Name"))

  comparetons <- txtCatchtons %>%
    dplyr::left_join(yearcatchtons, by = c("Code" = "species", "year" = "year")) %>%
    ggplot2::ggplot() +
    geom_line(aes(year, atoutput)) +
    geom_point(aes(year, yeartot), color = "blue", alpha = 0.2) +
    facet_wrap( ~ species, scales = "free_y")

  # looks like a match!
  comparetons

}

comparecatch(atlmod = atlmod, 
             select_groups = select_groups,
             stepperyr = stepperyr)

```

Now try the Isaac's recent CC model:

```{r, message=FALSE, warning=FALSE}
## CC

atlmod <- here("config/CCConfigSep22.R")

select_groups <- c("Arrowtooth_flounder",
                   "Petrale_sole",
                   "Pacific_sardine",
                   "Anchovy",
                   "Herring",
                   "Pacific_Ocean_Perch",
                   "Bocaccio_rockfish",
                   "Yelloweye_rockfish",
                   "Mesopel_M_Fish", #Pacific hake
                   "Mesopel_N_Fish", #Sablefish
                   "Demersal_P_Fish") #Dover sole

comparecatch(atlmod = atlmod, 
             select_groups = select_groups,
             stepperyr = stepperyr)
```

And finally the NEUS model, thanks to Joe for output files:

```{r, message=FALSE, warning=FALSE}
## NEUS
atlmod <- here("config/NEUStestConfigMay23.R")

select_groups <- c("Summerflounder",
                   "Winterflounder",
                   "Mackerel",
                   "Herring",
                   "Cod",
                   "Monkfish",
                   "Haddock",
                   "Spiny_Dogfish",
                   "Winter_Skate",
                   "Yellowtail_Flounder",
                   "Silver_Hake")

comparecatch(atlmod = atlmod, 
             select_groups = select_groups,
             stepperyr = stepperyr)

```

Looks like we have a match to CATCH.txt output for all systems using the same function and inputs from the CATCH.nc file. However, it looks like there is a final value in CATCH.txt that is not present, or not being summed correctly in the CATCH.nc output in the CC and NEUS models. Worth investigating...

### 3. Incorporate new `load_nc_catchtons` function into `run_truth`
